251 MA

### 2023-03-02 code/process.Rmd
more exploring

```{r, eval=F}
tier2_predint <- brm(pred_int ~ z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
                          z_log_ratio_ss + is_within + single_vignette + z_log_sample + z_log_trials + 
                          (z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
                          z_log_ratio_ss + is_within + single_vignette + z_log_sample + z_log_trials | academic_year),
                        family="bernoulli",
                        data=data_tier2,
                        file=here(model_location, "tier2_predint"),
                        prior=priors, 
                        control=list(adapt_delta=.99),
                        backend="cmdstanr")
```

>>>>

## Exploring stuff for Tier 1

```{r, eval=F}

strong_priors <- c(set_prior("horseshoe(3, par_ratio=.33)", class="b"),
            set_prior("normal(0,.5)", class="sd"),
            set_prior("lkj(1)", class="cor"))
tier1_subjective_strong_prior<- brm(sub_rep ~ z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
                          z_log_ratio_ss + is_within + single_vignette + z_log_sample + z_log_trials + 
                          (z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
                          z_log_ratio_ss + is_within + single_vignette + z_log_sample + z_log_trials | academic_year),
                        family="cumulative", # runs on 1-5 data
                        data=data_tier1,
                        file=here(model_location, "tier1_subjective_prior"),
                        prior=strong_priors, 
                        control=list(adapt_delta=.99),
                        backend="cmdstanr"
                        )
```

```{r, eval=F}

strong_priors_no_ranef <- c(set_prior("horseshoe(3, par_ratio=.33)", class="b"),
            set_prior("normal(0,.5)", class="sd"))
tier1_subjective_strong_prior<- brm(sub_rep ~ z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
                          z_log_ratio_ss + is_within + single_vignette + z_log_sample + z_log_trials + 
                          (1 | academic_year),
                        family="cumulative", # runs on 1-5 data
                        data=data_tier1,
                        file=here(model_location, "tier1_subjective_prior_no_ranef"),
                        prior=strong_priors_no_ranef, 
                        control=list(adapt_delta=.99),
                        backend="cmdstanr"
                        )
```

# bad linear

tier1_subjective_linear<- brm(sub_rep ~ z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
                          z_log_ratio_ss + is_within + single_vignette + z_log_sample + z_log_trials + 
                          (z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
                          z_log_ratio_ss + is_within + single_vignette + z_log_sample + z_log_trials | academic_year),
                       # family="cumulative", # runs on 1-5 data
                        data=data_tier1 |> mutate(sub_rep=(sub_rep-1)/4),
                        file=here(model_location, "tier1_subjective_linear"),
                        prior=strong_priors, 
                        control=list(adapt_delta=.99),
                        backend="cmdstanr"
                        )

tier1_subjective_linear2<- brm(sub_rep ~ z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
                          z_log_ratio_ss + is_within + single_vignette + z_log_sample + z_log_trials + 
                          (z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
                          z_log_ratio_ss + is_within + single_vignette + z_log_sample + z_log_trials | academic_year),
                       # family="cumulative", # runs on 1-5 data
                        data=data_tier1 |> mutate(sub_rep=(sub_rep-1)/4),
                        file=here(model_location, "tier1_subjective_linear2"),
                        prior=priors, 
                        control=list(adapt_delta=.99),
                        backend="cmdstanr"
                        )
```

```{r}
tier1_subjective_beta<- brm(sub_rep ~ z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
                          z_log_ratio_ss + is_within + single_vignette + z_log_sample + z_log_trials + 
                          (z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
                          z_log_ratio_ss + is_within + single_vignette + z_log_sample + z_log_trials | academic_year),
                        family="beta", # runs on 1-5 data
                        data=data_tier1 |> mutate(sub_rep=(sub_rep-1)/4*.98+.01),
                        file=here(model_location, "tier1_subjective_beta"),
                        prior=strong_priors, 
                        control=list(adapt_delta=.99),
                        backend="cmdstanr"
                        )

### frequentism

boring_logistic <- glm(sub_rep ~ z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
                          z_log_ratio_ss + is_within + single_vignette + z_log_sample + z_log_trials,
                        family=binomial, 
                        data=data_tier1 |> mutate(sub_rep=(sub_rep-1)/4),

                        )
library(glmnet)

predictors <- data_tier1 |> select(z_pub_year, open_data, open_mat, stanford, change_platform, 
                          z_log_ratio_ss, is_within, single_vignette, z_log_sample, z_log_trials)

yvals <- data_tier1 |> mutate(sub_rep=(sub_rep-1)/4) |> pull(sub_rep)
lasso_linear <- cv.glmnet(predictors, yvals |> as.matrix(), 
                        family="gaussian", alpha=1)

lasso_linear2 <- glmnet(predictors, yvals, 
                        family="gaussian", alpha=1)
```

## correlation

```{r}
library("lattice")
dat <- data_tier1 |> mutate(is.cog=ifelse(subfield=="cognitive", 1,0),
                            is.soc=ifelse(subfield=="social", 1,0),
                            is.other=ifelse(subfield=="other-psych", 1,0),
                            is.non=ifelse(subfield=="non-psych",1,0)) |> 
  select(is.cog, is.soc, is.other, is.non, z_pub_year, open_data, open_mat, stanford, change_platform, 
                          z_log_ratio_ss, is_within, single_vignette, z_log_sample, z_log_trials)

corr_mat <- round(cor(dat),2)

# Install and load reshape2 package
library(reshape2)

# reduce the size of correlation matrix
melted_corr_mat <- melt(corr_mat)
# head(melted_corr_mat)

# plotting the correlation heatmap
library(ggplot2)
ggplot(data = melted_corr_mat, aes(x=Var1, y=Var2,
                                   fill=value)) + scale_fill_viridis()+
geom_tile(alpha=.7)+theme(axis.text.x = element_text(angle = 40, vjust = 1, hjust=1))+geom_text(aes(label=value), size=3)

corr_mat |> as_tibble(rownames="value2") |> pivot_longer(cols=!value2, names_to="value1", values_to = "corr") |> arrange(corr) |> filter(value2 <value1) |> View()

corr_mat |> as_tibble(rownames="value2") |> pivot_longer(cols=!value2, names_to="value1", values_to = "corr") |> arrange(desc(corr)) |> filter(value2 <value1)

## Tier 2 and 3
```{r, eval=F}
tier2_predint <- brm(pred_int ~ z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
                          z_log_ratio_ss + is_within + single_vignette + z_log_sample + z_log_trials + 
                          (z_pub_year + subfield + open_data +  open_mat + stanford + change_platform + 
                          z_log_ratio_ss + is_within + single_vignette + z_log_sample + z_log_trials | academic_year),
                        family="bernoulli",
                        data=data_tier2,
                        file=here(model_location, "tier2_predint"),
                        prior=priors, 
                        control=list(adapt_delta=.99),
                        backend="cmdstanr")
```
